\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-11-15 chapters/stbf_struct.tex
Proofread mathematical notation

  \emph{This chapter was
  published as~\textcite{VanDenKerchove2022}.}

@@

	\section{Materials \& methods}
	\subsection{Notation}
	We represent matrices with bold capital letters, vectors with bold
	lowercase letters, fixed scalars with uppercase cursive letters and variable
  scalars with cursive lowercase letters.
	The epoched \ac{eeg} data with $N$ epochs, $C$ channels, and $S$ samples are
  represented in epoch format as $\{\mat{X}_i\in\mathbb{R}^{C\times S}\}^N_{i=1}$
  or flattened vector format by concatenating all channels for each epoch.
	Flattening results in $\{\mat{x}_i\in\mathbb{R}^{CS}\}^N_{i=1}$ such that
  $\mat{x}_i = \text{vec}(\mat{X}_i)$.
	The real covariance matrix of the epochs in vector format is
  denoted by $\mat{C}$, estimators thereof as $\hat{\mat{C}}$.

@@

	For the following analyses, we assume that all \ac{eeg} channels are normalized with zero mean and unit variance without loss of generality.
	Solving \cref{eq:stbf-struct/minimum-variance} under the linear constraint given by
  \cref{eq:stbf-struct/linear-constraint} returns the filter weights $\mat{w}$ defining the spatiotemporal \ac{lcmv}-beamformer.
	\begin{equation}
    \argmin_\mat{w}\mat{w}^\intercal \mat{C}
		\mat{w}^\intercal
		\label{eq:stbf-struct/minimum-variance}
	\end{equation}
	\begin{equation}
		\mat{a}^\intercal\mat{w} = 1
		\label{eq:stbf-struct/linear-constraint}
	\end{equation}
	These weights minimize the variance of the output of the filter while enhancing
	the signal characterized by the constraint.
  $\mat{a} = \text{vec}(\mat{A})$ is the data-driven activation pattern, a template
	of the signal of interest maximizing the difference between two classes of
	epochs, determined as follows:
	\begin{equation}
		\mathbf{a} =
		\frac{1}{|\text{class 1}|}\sum_\text{class 1}\mathbf{x_i} -
		\frac{1}{|\text{class 2}|}\sum_\text{class 2}\mathbf{x_i}
		\label{eq:stbf-struct/ap}
	\end{equation}

	The method of Lagrange multipliers then gives the closed-form solution to the minimization problem posed by
	\cref{eq:stbf-struct/minimum-variance} and \cref{eq:stbf-struct/linear-constraint} as:
	\begin{equation}
		\mat{w} =
    \frac{\mat{C}^{-1}\mat{a}^\intercal}
    {\mat{a}\mat{C}^{-1}\mat{a}^\intercal}
		\label{eq:stbf-struct/closed-form}
	\end{equation}
	The beamformer can be applied to epochs (unseen or not) as:
	\begin{equation}
		y_i = \mathbf{w}\mathbf{x}_i
		\label{eq:stbf-struct/apply-bf}
	\end{equation}
	resulting in a scalar output per epoch.
	The linear constraint in \cref{eq:stbf-struct/linear-constraint} ensures that the
	beamformer maps epochs containing a target response to a score close to one
	and, conversely, epochs not containing a target response to a score close to
	zero.

@@

	\subsubsection{Empirical covariance estimation}
	\label{sec:stbf-struct/methods/emp-cov}
	Earlier spatiotemporal beamformer studies~\cite{Wittevrongel2016,
		Wittevrongel2016a, Wittevrongel2017, Wittevrongel2017a} use the empirical
	covariance and inverse covariance calculated as follows:
	\begin{equation}
    \hat{\mat{C}}_\text{emp} =
		\frac{1}{N-1}\sum^{N}_{i=1}\mat{x}_i\mat{x}_i^\intercal
		\label{eq:stbf-struct/emp-cov}
	\end{equation}
	\begin{equation}
    \widehat{\mat{C}^{-1}}_\text{emp} = \hat{\mat{C}}_\text{emp}^+
		\label{eq:stbf-struct/emp-inv-cov}
	\end{equation}
	The Moore-Penrose pseudoinverse $^+$, ensures a solution exists when
  $\hat{\mat{C}}_\text{emp}$ is singular.
	\cref{fig:kronlda-covs}a and \cref{fig:kronlda-covs}b respectively show examples of the
	empirical estimators of the covariance and the inverse covariance matrices.
	The empirical estimator suffers from performance and
	stability issues if the number of epochs $N$ used or estimation is not much larger than the number of features $CS$~\cite{Stein1956,Khatri1987}.

@@

	Earlier work~\cite{Libert2021} applied shrinkage regularization to \ac{erp}
	decoding with the spatiotemporal beamformer and showed competitive performance
	compared to other state-of-the-art decoding techniques like stepwise LDA or SVM.
	The abovementioned work chooses the shrinkage coefficient $\alpha$ as a fixed hyperparameter.
	However, its optimal value depends on the number of training epochs, the
	covariance matrix's dimensionality, and the independence and variance of the
	data, which can vary across evaluation settings and per session.
	The optimal value for $\alpha$ can be found with a line search using cross-validation, but this can be a costly procedure.
	Methods exist to estimate an optimal shrinkage value from the data directly.
	Most notable among these are the Ledoit-Wolf procedure~\cite{Ledoit2004},
	Rao-Blackwell Ledoit-Wolf~\cite{Chen2010}, and Oracle Approximating Shrinkage~\cite{Chen2010}.
	A more recent estimation method~\cite{Tong2018} emulates a leave-one-out
	cross-validation (\ac{loocv}) scheme expressed by the data-driven closed-form
	estimate:
	\begin{equation}
		\alpha =
		1-\frac{
      \frac{N}{N-1}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			- \frac{1}{N(N-1)}\sum_{i=1}^N||\mat{x}_i||_2^4
		}
		{
      \frac{N^2 -2N}{(N-1)^2}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			+ \frac{1}{N(N-1)^2}\sum_{i=1}^N||\mat{x}_i||_2^4
		}
		\label{eq:loocv}
	\end{equation}

	We opt for the \ac{loocv} shrinkage estimator because it avoids some of the
	assumptions made by~\cite{Ledoit2004} and~\cite{Chen2010} and
	because it generalizes to structured covariance estimation as described in
	\cref{sec:stbf-struct/methods/structured-estimation}.

@@

	Finally, based on \cref{propr:stbf-struct/kron-multiplication},
	\cref{eq:stbf-struct/closed-form} can be reformulated more efficiently as
	\cref{eq:stbf-struct/closed-form-kron}.
	\begin{property}
    $(\mat{U}\otimes \mat{V})\cdot\text{vec}(\mat{W}) =
    \text{vec}(\mat{V}\mat{W}\mat{U}^\intercal)$
    for any matrices $\mat{U}\in\mathbb{R}^{P\times P}$,
    $\mat{V}\in\mathbb{R}^{Q\times Q}$ and $\mat{W}\in\mathbb{R}^{P\times Q}$~\cite{Loan2000}.
		\label{propr:stbf-struct/kron-multiplication}
	\end{property}

	\begin{equation}
		\hat{\mat{w}}_\text{struct} =
    \frac{\hat{\mat{S}}^+\mat{A}^\intercal\hat{\mat{T}}^+}
    {\mat{a}\cdot\text{vec}(\hat{\mat{S}}^+A^\intercal\hat{\mat{T}}^+)}
		\label{eq:stbf-struct/closed-form-kron}
	\end{equation}

@@

	Combined, this leads to the iterative estimation algorithm described by the
	following equations:
	\begin{subequations}
		\begin{equation}
      \tilde{\mat{S}}_{k+1} =
			\frac{1}{N}
      \sum^N_{i=1}\mat{X}_i^\intercal\hat{\mat{T}}_k^+\mat{X}_i
			\label{eq:stbf-struct/fpi-spatial}
		\end{equation}
		\begin{equation}
      \tilde{\mat{T}}_{k+1} =
			\frac{1}{N}
      \sum^N_{i=1}\mat{X}_i\hat{\mat{S}}_k^+\mat{X}_i^\intercal
			\label{eq:stbf-struct/fpi-temporal}
		\end{equation}
	\end{subequations}
	\begin{subequations}
		\begin{equation}
      \tilde{\mat{S}}_{k+1}^{(\beta)} =
      (1-\beta_{k+1})\tilde{\mat{S}}_{k+1}
      +\beta_{k+1}\frac{\text{Tr}(\tilde{\mat{S}}_{k+1})}{C}\mathbb{I}
			\label{eq:stbf-struct/fpi-spatial-shrunk}
		\end{equation}
		\begin{equation}
      \tilde{\mat{T}}_{k+1}^{(\gamma)} =
      (1-\gamma_{k+1})\tilde{\mat{T}}_{k+1}
      +\gamma_{k+1}\frac{\text{Tr}(\tilde{\mat{T}}_{k+1})}{S}\mathbb{I}
			\label{eq:stbf-struct/fpi-temporal-shrunk}
		\end{equation}
	\end{subequations}
	\begin{subequations}
		\begin{equation}
      \hat{\mat{S}}_{k+1} =
      \frac{C}{\text{Tr}\left[\tilde{\mat{S}}_{k+1}^{(\beta)}\right]}
      \tilde{\mat{S}}_{k+1}^{(\beta)}
			\label{eq:stbf-struct/fpi-spatial-norm}
		\end{equation}
		\begin{equation}
      \hat{\mat{T}}_{k+1} =
      \frac{S}{\text{Tr}\left[\tilde{\mat{T}}_{k+1}^{(\gamma)}\right]}
      \tilde{\mat{T}}_{k+1}^{(\gamma)}
			\label{eq:stbf-struct/fpi-temporal-norm}
		\end{equation}
	\end{subequations}
  $\hat{\mat{S}}_0$ and $\hat{\mat{T}}_0$ can be initialized to any positive definite matrix.
	We choose to use the identity matrices $\mathbb{I}^{C\times C}$ and $\mathbb{I}^{S\times S}$.
  After each iteration, all diagonals of $\hat{\mat{R}}_{k+1}$ are set to their mean
  values to ensure that $\hat{\mat{R}}_{k+1}$ and $\hat{\mat{T}}_{k+1}$ are Toeplitz structured.

@@

	\begin{subequations}
		\begin{equation}
			\beta_{k+1} =
			1-
			\frac{
        \frac{N}{N-1}\text{Tr}(\tilde{\hat{S}}_{k+1}^2)
        - \frac{2}{C}\left[\text{Tr}(\tilde{\mat{S}}_{k+1})\right]^2
        + \frac{1}{C}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
				- \frac{1}{N(N-1)}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i\hat{\mat{T}}_k^+\mat{X}_i^\intercal)^2\right]
			}{
        \frac{N^2-2N}{(N-1)^2}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
        - \frac{2}{C}\left[\text{Tr}(\tilde{\mat{S}}_{k+1})\right]^2
        + \frac{1}{C}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
				+ \frac{1}{N(N-1)^2}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i\hat{\mat{T}}_k^+\mat{X}_i^\intercal)^2\right]
			}
			\label{eq:stbf-struct/spatial-shrinkage}
		\end{equation}
		\begin{equation}
			\gamma_{k+1} =
			1-
			\frac{
        \frac{N}{N-1}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
        - \frac{2}{S}\left[\text{Tr}(\tilde{\mat{T}}_{k+1})\right]^2
				+ \frac{1}{S}\text{Tr}(\tilde{T}_{k+1}^2)
				- \frac{1}{N(N-1)}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i^\intercal\mat{\mat{S}}_k^+\mat{X}_i)^2\right]
			}{
        \frac{N^2-2N}{(N-1)^2}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
        - \frac{2}{S}\left[\text{Tr}(\tilde{\mat{T}}_{k+1})\right]^2
        + \frac{1}{S}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
				+ \frac{1}{N(N-1)^2}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i^\intercal\hat{\mat{S}}_k^+\mat{X}_i)^2\right]
			}
			\label{eq:stbf-struct/temporal-shrinkage}
		\end{equation}
	\end{subequations}
	The shrinkage parameters $0<\beta_{k+1}<1$ and $0<\gamma_{k+1}<1$ should be
	re-determined after each iteration.
	The Oracle Approximation Shrinkage method can also be used to determine
	$\beta_{k+1}$ and $\gamma_{k+1}$~\cite{Chen2010,Xie2021} but performs worse for spatiotemporal \ac{eeg} data since not all assumptions are met.

@@

    \begin{subfigure}{\linewidth}
      \input{figures/stbf_struct/fpi-1.pgf}
      \caption{Results for 1, 2, and 5 trials using all nine training blocks in
      the training folds.}
    \end{subfigure}
    \caption[Average cross-validated \textsc{stbf-struct} accuracy]{%
      Average cross-validated \textsc{stbf-struct} accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Error bars represent the first and third quartiles. The
      accuracy does not improve when using more than one iteration.}
		\label{fig:iterations}
	\end{figure}

>>>>

  \noindent\emph{This chapter was
  published as~\textcite{VanDenKerchove2022}.}

@@

	\section{Materials \& methods}
	\subsection{Notation}
	We represent matrices with bold capital letters, vectors with bold
	lowercase letters, fixed scalars with uppercase cursive letters and variable
  scalars with cursive lowercase letters.
	The epoched \ac{eeg} data with $N$ epochs, $C$ channels, and $S$ samples are
  represented in epoch format as $\{\mat{X}_n\in\mathbb{R}^{C\times S}\}^N_{n=1}$
  or flattened vector format by concatenating all channels for each epoch.
	Flattening results in $\{\mat{x}_n\in\mathbb{R}^{CS}\}^N_{n=1}$ such that
  $\mat{x}_n = \text{vec}(\mat{X}_n)$.
	The real covariance matrix of the epochs in vector format is
  denoted by $\mat{C}$, estimators thereof as $\hat{\mat{C}}$.

@@

	For the following analyses, we assume that all \ac{eeg} channels are normalized with zero mean and unit variance without loss of generality.
	Solving \cref{eq:stbf-struct/minimum-variance} under the linear constraint given by
  \cref{eq:stbf-struct/linear-constraint} returns the filter weights $\mat{w}$ defining the spatiotemporal \ac{lcmv}-beamformer.
	\begin{equation}
    \argmin_\mat{w}\mat{w}^\intercal \mat{C}
		\mat{w}^\intercal
		\label{eq:stbf-struct/minimum-variance}
	\end{equation}
	\begin{equation}
		\mat{a}^\intercal\mat{w} = 1
		\label{eq:stbf-struct/linear-constraint}
	\end{equation}
	These weights minimize the variance of the output of the filter while enhancing
	the signal characterized by the constraint.
  $\mat{a} = \text{vec}(\mat{A})$ is the data-driven activation pattern, a template
	of the signal of interest maximizing the difference between two classes of
	epochs, determined as follows:
	\begin{equation}
		\mathbf{a} =
		\frac{1}{|\text{class 1}|}\sum_\text{class 1}\mathbf{x_n} -
		\frac{1}{|\text{class 2}|}\sum_\text{class 2}\mathbf{x_n}
		\label{eq:stbf-struct/ap}
	\end{equation}

	The method of Lagrange multipliers then gives the closed-form solution to the minimization problem posed by
	\cref{eq:stbf-struct/minimum-variance} and \cref{eq:stbf-struct/linear-constraint} as:
	\begin{equation}
		\mat{w} =
    \frac{\mat{C}^{-1}\mat{a}^\intercal}
    {\mat{a}\mat{C}^{-1}\mat{a}^\intercal}
		\label{eq:stbf-struct/closed-form}
	\end{equation}
	The beamformer can be applied to epochs (unseen or not) as:
	\begin{equation}
		y_n = \mathbf{w}\mathbf{x}_n
		\label{eq:stbf-struct/apply-bf}
	\end{equation}
	resulting in a scalar output per epoch.
	The linear constraint in \cref{eq:stbf-struct/linear-constraint} ensures that the
	beamformer maps epochs containing a target response to a score close to one
	and, conversely, epochs not containing a target response to a score close to
	zero.

@@

	\subsubsection{Empirical covariance estimation}
	\label{sec:stbf-struct/methods/emp-cov}
	Earlier spatiotemporal beamformer studies~\cite{Wittevrongel2016,
		Wittevrongel2016a, Wittevrongel2017, Wittevrongel2017a} use the empirical
	covariance and inverse covariance calculated as follows:
	\begin{equation}
    \hat{\mat{C}}_\text{emp} =
		\frac{1}{N-1}\sum^{N}_{n=1}\mat{x}_n\mat{x}_in\intercal
		\label{eq:stbf-struct/emp-cov}
	\end{equation}
	\begin{equation}
    \widehat{\mat{C}^{-1}}_\text{emp} = \hat{\mat{C}}_\text{emp}^+
		\label{eq:stbf-struct/emp-inv-cov}
	\end{equation}
	The Moore-Penrose pseudoinverse, $^+$, ensures a solution exists when
  $\hat{\mat{C}}_\text{emp}$ is singular.
	\cref{fig:kronlda-covs}a and \cref{fig:kronlda-covs}b respectively show examples of the
	empirical estimators of the covariance and the inverse covariance matrices.
	The empirical estimator suffers from performance and
	stability issues if the number of epochs $N$ used or estimation is not much larger than the number of features $CS$~\cite{Stein1956,Khatri1987}.

@@

	Earlier work~\cite{Libert2021} applied shrinkage regularization to \ac{erp}
	decoding with the spatiotemporal beamformer and showed competitive performance
	compared to other state-of-the-art decoding techniques like stepwise LDA or SVM.
	The abovementioned work chooses the shrinkage coefficient $\alpha$ as a fixed hyperparameter.
	However, its optimal value depends on the number of training epochs, the
	covariance matrix's dimensionality, and the independence and variance of the
	data, which can vary across evaluation settings and per session.
	The optimal value for $\alpha$ can be found with a line search using cross-validation, but this can be a costly procedure.

	Methods exist to estimate an optimal shrinkage value from the data directly.
	Most notable among these are the Ledoit-Wolf procedure~\cite{Ledoit2004},
	Rao-Blackwell Ledoit-Wolf~\cite{Chen2010}, and Oracle Approximating Shrinkage~\cite{Chen2010}.
  A more recent estimation method~\cite{Tong2018} emulates a \ac{loocv} scheme expressed by the data-driven closed-form
	estimate:
	\begin{equation}
		\alpha =
		1-\frac{
      \frac{N}{N-1}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			- \frac{1}{N(N-1)}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		{
      \frac{N^2 -2N}{(N-1)^2}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			+ \frac{1}{N(N-1)^2}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		\label{eq:loocv}
	\end{equation}
	We opt for the \ac{loocv} shrinkage estimator because it avoids some of the
	assumptions made by~\cite{Ledoit2004} and~\cite{Chen2010} and
	because it generalizes to structured covariance estimation as described in
	\cref{sec:stbf-struct/methods/structured-estimation}.

@@

	Finally, based on \cref{propr:stbf-struct/kron-multiplication},
	\cref{eq:stbf-struct/closed-form} can be reformulated more efficiently as
	\cref{eq:stbf-struct/closed-form-kron}.
	\begin{property}
    $(\mat{U}\otimes \mat{V})\cdot\vect(\mat{W}) =
    \vect(\mat{V}\mat{W}\mat{U}^\intercal)$
    for any matrices $\mat{U}\in\mathbb{R}^{P\times P}$,
    $\mat{V}\in\mathbb{R}^{Q\times Q}$ and $\mat{W}\in\mathbb{R}^{P\times Q}$~\cite{Loan2000}.
		\label{propr:stbf-struct/kron-multiplication}
	\end{property}

	\begin{equation}
		\hat{\mat{w}}_\text{struct} =
    \frac{\hat{\mat{S}}^+\mat{A}^\intercal\hat{\mat{T}}^+}
    {\mat{a}\cdot\vect\left(\hat{\mat{S}}^+A^\intercal\hat{\mat{T}}^+\right)}
		\label{eq:stbf-struct/closed-form-kron}
	\end{equation}

@@

	Combined, this leads to the iterative estimation algorithm described by the
	following equations:
	\begin{subequations}
		\begin{equation}
      \tilde{\mat{S}}_{k+1} =
			\frac{1}{N}
      \sum^N_{n=1}\mat{X}_n^\intercal\hat{\mat{T}}_k^+\mat{X}_n
			\label{eq:stbf-struct/fpi-spatial}
		\end{equation}
		\begin{equation}
      \tilde{\mat{T}}_{k+1} =
			\frac{1}{N}
      \sum^N_{n=1}\mat{X}_n\hat{\mat{S}}_k^+\mat{X}_n^\intercal
			\label{eq:stbf-struct/fpi-temporal}
		\end{equation}
	\end{subequations}
	\begin{subequations}
		\begin{equation}
      \tilde{\mat{S}}_{k+1}^{(\beta)} =
      (1-\beta_{k+1})\tilde{\mat{S}}_{k+1}
      +\beta_{k+1}\frac{\text{Tr}(\tilde{\mat{S}}_{k+1})}{C}\mathbb{I}
			\label{eq:stbf-struct/fpi-spatial-shrunk}
		\end{equation}
		\begin{equation}
      \tilde{\mat{T}}_{k+1}^{(\gamma)} =
      (1-\gamma_{k+1})\tilde{\mat{T}}_{k+1}
      +\gamma_{k+1}\frac{\text{Tr}(\tilde{\mat{T}}_{k+1})}{S}\mathbb{I}
			\label{eq:stbf-struct/fpi-temporal-shrunk}
		\end{equation}
	\end{subequations}
	\begin{subequations}
		\begin{equation}
      \hat{\mat{S}}_{k+1} =
      \frac{C}{\text{Tr}\left[\tilde{\mat{S}}_{k+1}^{(\beta)}\right]}
      \tilde{\mat{S}}_{k+1}^{(\beta)}
			\label{eq:stbf-struct/fpi-spatial-norm}
		\end{equation}
		\begin{equation}
      \hat{\mat{T}}_{k+1} =
      \frac{S}{\text{Tr}\left[\tilde{\mat{T}}_{k+1}^{(\gamma)}\right]}
      \tilde{\mat{T}}_{k+1}^{(\gamma)}
			\label{eq:stbf-struct/fpi-temporal-norm}
		\end{equation}
	\end{subequations}
  $\hat{\mat{S}}_0$ and $\hat{\mat{T}}_0$ can be initialized to any positive definite matrix.
	We choose to use the identity matrices $\mathbb{I}^{C\times C}$ and $\mathbb{I}^{S\times S}$.
  After each iteration, all diagonals of $\hat{\mat{R}}_{k+1}$ are set to their mean
  values to ensure that $\hat{\mat{R}}_{k+1}$ and $\hat{\mat{T}}_{k+1}$ are Toeplitz structured.

@@

	\begin{subequations}
		\begin{equation}
			\beta_{k+1} =
			1-
			\frac{
        \frac{N}{N-1}\text{Tr}(\tilde{\mat{\hat{\S}}}_{k+1}^2)
        - \frac{2}{C}\left[\text{Tr}(\mat{\tilde{S}}_{k+1})\right]^2
        + \frac{1}{C}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
				- \frac{1}{N(N-1)}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i\hat{\mat{T}}_k^+\mat{X}_i^\intercal)^2\right]
			}{
        \frac{N^2-2N}{(N-1)^2}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
        - \frac{2}{C}\left[\text{Tr}(\tilde{\mat{S}}_{k+1})\right]^2
        + \frac{1}{C}\text{Tr}(\tilde{\mat{S}}_{k+1}^2)
				+ \frac{1}{N(N-1)^2}\sum_{i=1}^N
        \left[\text{Tr}(\mat{X}_i\hat{\mat{T}}_k^+\mat{X}_i^\intercal)^2\right]
			}
			\label{eq:stbf-struct/spatial-shrinkage}
		\end{equation}
		\begin{equation}
			\gamma_{k+1} =
			1-
			\frac{
        \frac{N}{N-1}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
        - \frac{2}{S}\left[\text{Tr}(\tilde{\mat{T}}_{k+1})\right]^2
        + \frac{1}{S}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
				- \frac{1}{N(N-1)}\sum_{n=1}^N
        \left[\text{Tr}(\mat{X}_n^\intercal\mat{\mat{S}}_k^+\mat{X}_n)^2\right]
			}{
        \frac{N^2-2N}{(N-1)^2}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
        - \frac{2}{S}\left[\text{Tr}(\tilde{\mat{T}}_{k+1})\right]^2
        + \frac{1}{S}\text{Tr}(\tilde{\mat{T}}_{k+1}^2)
				+ \frac{1}{N(N-1)^2}\sum_{n=1}^N
        \left[\text{Tr}(\mat{X}_n^\intercal\hat{\mat{S}}_k^+\mat{X}_n)^2\right]
			}
			\label{eq:stbf-struct/temporal-shrinkage}
		\end{equation}
	\end{subequations}
	The shrinkage parameters $0<\beta_{k+1}<1$ and $0<\gamma_{k+1}<1$ should be
	re-determined after each iteration.
	The Oracle Approximation Shrinkage method can also be used to determine
	$\beta_{k+1}$ and $\gamma_{k+1}$~\cite{Chen2010,Xie2021} but performs worse for spatiotemporal \ac{eeg} data since not all assumptions are met.

@@

    \begin{subfigure}{\linewidth}
      \input{figures/stbf_struct/fpi-1.pgf}
      \caption{Results for 1, 2, and 5 trials using all nine training blocks in
      the training folds.}
    \end{subfigure}
    \caption[Average cross-validated \textsc{stbf-struct} accuracy]{%
      Average cross-validated \textsc{stbf-struct} accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Shaded area represents a 95\% confidenced interval obtained
      through 1000 bootstrapping iterations.
      Accuracy does not improve when using more than one iteration.}
		\label{fig:iterations}
	\end{figure}
